---

title: "| Assignment 4: Collaborating Together\n| Introduction to Applied Data Science\n|

  2022-2023\n"

author: |

  | Ana Sofia Polo Bleher

  | a.s.polobleher@students.uu.nl

  | http://www.github.com/anableher1

date: "June 2023"

output:

  html_document:

    df_print: paged

linkcolor: purple

urlcolor: purple

---

 

```{r setup, include = FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=TRUE)

```

 

## Assignment 4: Collaborating Together

 

### Part 1: Contributing to another student's Github repository

 

In this assignment, you will create a Github repository, containing this document and the .pdf output, which analyzes a dataset individually using some of the tools we have developed.

 

This time, make sure to not only put your name and student e-mail in your Rmarkdown header, but also your Github account, as I have done myself.

 

However, you will also pair up with a class mate and contribute to each others' Github repository. Each student is supposed to contribute to another student's work by writing a short interpretation of 1 or 2 sentences at the designated place (this place is marked with **designated place**) in the other student's assignment.

 

This interpretation will not be graded, but a Github shows the contributors to a certain repository. This way, we can see whether you have contributed to a repository of a class mate.

 

**Question 1.1**: Fill in the __github username__ of the class mate to whose repository you have contributed.

 

kayverduynlunel

 

### Part 2: Analyzing various linear models

 

In this part, we will summarize a dataset and create a couple of customized tables. Then, we will compare a couple of linear models to each other, and see which linear model fits the data the best, and yields the most interesting results.

 

We will use a dataset called `GrowthSW` from the `AER` package. This is a dataset containing 65 observations on 6 variables and investigates the determinants of economic growth. First, we will try to summarize the data using the `modelsummary` package.

 

```{r, warning=FALSE, message=FALSE}

library(AER)

data(GrowthSW)

```

 

One of the variables in the dataset is `revolutions`, the number of revolutions, insurrections and coup d'etats in country $i$ from 1965 to 1995.

 

**Question 2.1**: Using the function `datasummary`, summarize the mean, median, sd, min, and max of the variables `growth`, and `rgdp60` between two groups: countries with `revolutions` equal to 0, and countries with more than 0 revolutions. Call this variable `treat`. Make sure to also write the resulting data set to memory. Hint: you can check some examples [here](https://vincentarelbundock.github.io/modelsummary/articles/datasummary.html#datasummary).

 

```{r}

library(modelsummary); library(tidyverse)

 

library(dplyr)

 

 

#Add the variable treat to the dataset

 

GrowthSW <- GrowthSW %>%

  mutate(treat = ifelse(GrowthSW$revolutions > 0, "Revolutionary", "Non-revolutionary"))

 

#Create separate datasets for revolutionary and non-revolutionary countries

 

RevGrowthSW <- GrowthSW %>%

  filter(treat == "Revolutionary")

 

UnrevgrowthSW <- GrowthSW %>%

  filter(treat == "Non-revolutionary")

 

#Perform the summaries on both groups

 

datasummary(growth +rgdp60 ~ Mean + Median + SD + Min + Max, data = RevGrowthSW)

 

datasummary(growth +rgdp60 ~ Mean + Median + SD + Min + Max, data = UnrevgrowthSW)

 

 

```
